### 2023-02-28 chapters/interpretability/imli/incremental_learning.tex
addressing kuldeep's comments
minor edit

\section{Incremental Learning with MaxSAT}
\label{interpretability_imli_sec:incremental_learning}
The complexity of the MaxSAT query in Section~\ref{interpretability_imli_sec:encoding} increases with the number of samples in the training dataset and the number of clauses to be learned in a CNF formula. In this section, we discuss an incremental learning technique that along with the MaxSAT formulation can generate classification rules efficiently. Our incremental learning is built on two concepts: (i)
mini-batch learning and (ii) iterative learning. We discuss both in detail in the following.

>>>>

\section{Incremental Learning with MaxSAT}
\label{interpretability_imli_sec:incremental_learning} 
To facilitate a scalable learning, we discuss the key technical contribution of this chapter: an incremental learning framework of interpretable classification rules based on MaxSAT. The complexity of the MaxSAT query in Section~\ref{interpretability_imli_sec:encoding} increases with the number of samples $ n $ in the training dataset and the number of clauses $ k $  in the CNF classifier. To scale on large $ n $ and $ k $, our incremental learning is built on two concepts: (i) mini-batch learning and (ii) iterative learning.
